Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
attempt to knit

### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade}
AR$G <- transactions$G %>%

@@

  mutate(
    confidence = support / lhs.rateTake.support,
    lift       = confidence / rhs.support
    )

>>>>

### grade less than or equal to x -> grade less than or equal to 6
```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

@@
